Cluster Difference Imaging Photometric Survey (CDIPS) II: A Jupiter-Sized Planet in IC~2602

### 2020-05-19 paper/ms.tex
minor updates
update
add simple calculation of prob BEB

\begin{figure}[t!]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.48\textwidth]{f2.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
    {\bf Phase-folded transit of \pn.} Gray points are
    2-minute PDCSAP flux measurements, detrended with
    a 0.3-day robust Huber spline (see Section~\ref{subsec:tess}).
    Black points are binned to approximately 1 point per 6 minutes.
    One hundred samples from the posterior are shown with orange lines.
    % The bottom panel shows the residuals.
    \label{fig:phasefold}
	}
\end{figure}

@@

  \item {\it Hierarchical blends}.
    Limited by i) FEROS + Veloce RVs, and ii) the star being nicely on the
    cluster HR diagram. Any extra hidden close-in binary stars would
    need to be very low-mass M dwarfs, and then the transit duration
    again helps.

  \item {\it Background blends}.
    Archival SERC-J and AAO-SES plates are available for the \tn\
    field\footnote{\url{https://archive.stsci.edu/cgi-bin/dss_form}}.
    These plates were acquired in 1982 and 1992, respectively.
    For high proper motion stars archival imagery can be used to
    detect slowly moving background stars that might be an
    astrophysical false-positive source
    ({\it e.g.}, \citealt{huang_pimen_2018}).
    However \tn\ has only moved $\approx0.7''$ between 1982 and
    present, in comparison to the $\approx2.0''$ FWHM of the target on
    the plates.
    We therefore cannot resolve it with great confidence from
    background sources not already resolved through more modern
    imaging.

>>>>

\begin{figure*}[t!]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.9\textwidth]{f2.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
    {\bf Phase-folded transit of \pn.} Gray points are
    2-minute PDCSAP flux measurements, detrended with
    a 0.3-day robust Huber spline (see Section~\ref{subsec:tess}).
    Black points are binned to approximately 1 point per 6 minutes.
    The blue line shows the transit model corresponding to the median
    transit parameters (Table~2).
    % The bottom panel shows the residuals.
    \label{fig:phasefold}
	}
\end{figure*}

@@

  \item {\it Hierarchical blends}.
    Limited by i) FEROS + Veloce RVs, and ii) the star being nicely on the
    cluster HR diagram. Any extra hidden close-in binary stars would
    need to be very low-mass M dwarfs, and then the transit duration
		(and lack of chromaticity???) again helps.

  \item {\it Background blends}.
	An argument on the a priori probability of background blends follows from
	counting statistics. Within 360 arcseconds, there are 298 T<16 stars in TIC8
	(i.e., Gaia DR2). At 2.0 arcseconds, SOAR archives dmag(I) of 6. Inside of 2
	arcseconds, we expect $\pi r^2 $ times (Nstar per sq arcsec) = 9e-3 T<16 stars.
	Any with T$\gtrsim$15 outside of 0.3 arcseconds would have been detected by
	SOAR, which brings down the expected number of possible hidden sources by a
	factor of a few.  Within 0.3 arcseconds, where SOAR gets worse than dmag(I) of
	3, we expect 2e-4 T<16 stars. So (order of magnitude), background blends would
	be a ~0.1\% coincidence.

    Archival SERC-J and AAO-SES plates are available for the \tn\
    field\footnote{\url{https://archive.stsci.edu/cgi-bin/dss_form}}.
    These plates were acquired in 1982 and 1992, respectively.
    For high proper motion stars archival imagery can be used to
    detect slowly moving background stars that might be an
    astrophysical false-positive source
    ({\it e.g.}, \citealt{huang_pimen_2018}).
    However \tn\ has only moved $\approx0.7''$ between 1982 and
    present, in comparison to the $\approx2.0''$ FWHM of the target on
    the plates.
    We therefore cannot resolve it with great confidence from
    background sources not already resolved through more modern
    imaging.
